### 2020-04-27 Temp_tables/Temp_tables_revision/02_table_7_improvement/wrong_cut_bin/031_PRIVATE_city.tex
back up before new paper

\begin{document}% Date and time: Fri, Mar 27, 2020 - 09:43:16
\begin{table}[!htbp] \centering 
  \caption{SOE dominating city} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{12}{c}{The Dependent variable:} \\ 
\cline{2-13} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11) & (12)\\
 \\[-1.8ex]& decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.187 & $-$0.283 & $-$0.247 & $-$0.068 & $-$0.084 & $-$0.225 & $-$0.205 & $-$0.032 & $-$0.146 & $-$0.266 & $-$0.236 & $-$0.206 \\ 
  & (0.160) & (0.174) & (0.208) & (0.247) & (0.155) & (0.172) & (0.174) & (0.270) & (0.155) & (0.175) & (0.184) & (0.258) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 19,884 & 13,240 & 10,516 & 7,465 & 20,004 & 12,942 & 13,062 & 7,528 & 19,730 & 13,214 & 12,226 & 6,668 \\ 
R$^{2}$ & 0.858 & 0.866 & 0.867 & 0.877 & 0.858 & 0.867 & 0.867 & 0.875 & 0.857 & 0.862 & 0.864 & 0.884 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{12}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{12}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{12}{l}{are clustered by city} \\ 
\end{tabular}
\end{adjustbox}
\end{table}

>>>>

\begin{document}% Date and time: Fri, Mar 27, 2020 - 09:44:16
\begin{table}[!htbp] \centering 
  \caption{Private dominating city} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{12}{c}{The Dependent variable:} \\ 
\cline{2-13} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11) & (12)\\
 \\[-1.8ex]& decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7 & decile .3 & median &  mean & decile .7\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.047 & $-$0.034 & $-$0.118 & $-$0.161 & $-$0.308 & $-$0.095 & $-$0.115 & $-$0.182 & $-$0.118 & $-$0.082 & $-$0.093 & $-$0.120 \\ 
  & (0.177) & (0.167) & (0.150) & (0.136) & (0.201) & (0.173) & (0.167) & (0.135) & (0.194) & (0.169) & (0.156) & (0.144) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 10,792 & 17,436 & 20,160 & 23,211 & 10,672 & 17,734 & 17,614 & 23,148 & 10,946 & 17,462 & 18,450 & 24,008 \\ 
R$^{2}$ & 0.865 & 0.856 & 0.856 & 0.854 & 0.867 & 0.855 & 0.855 & 0.854 & 0.868 & 0.859 & 0.859 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\textit{Note:}  & \multicolumn{12}{l}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\ 
 & \multicolumn{12}{l}{Heteroskedasticity-robust standard errors in parentheses} \\ 
 & \multicolumn{12}{l}{are clustered by city} \\ 
\end{tabular}
\end{adjustbox}
\end{table}

### 2020-04-27 Temp_tables/Temp_tables_revision/03_Paper_version_Revised/04bis_table_7_rob_3.tex
back up before new paper

\begin{document}% Date and time: Sat, Apr 04, 2020 - 11:27:39
\begin{table}[!htbp] \centering 
  \caption{Presence of Foreign firms} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.101 & $-$0.101 & $-$0.051 & 0.078 & 0.123 & 0.044 \\ 
  & (0.169) & (0.164) & (0.156) & (0.211) & (0.203) & (0.180) \\ 
   TCZ_c \times \text{Period} \times \text{output share Foreign}_{i} & $-$0.387 &  &  & 0.937 &  &  \\ 
  & (0.662) &  &  & (0.919) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share Foreign}_{i} & $-$0.299 &  &  & $-$1.448 &  &  \\ 
  & (1.019) &  &  & (1.237) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{capital share Foreign}_{i}  &  & $-$0.291 &  &  & 0.984 &  \\ 
  &  & (0.620) &  &  & (0.781) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share Foreign}_{i}  &  & $-$0.249 &  &  & $-$1.710 &  \\ 
  &  & (0.942) &  &  & (1.109) &  \\ 
   TCZ_c \times \text{Period} \times \text{labour share Foreign}_{i}  &  &  & 0.004 &  &  & 1.203 \\ 
  &  &  & (0.599) &  &  & (0.757) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share Foreign}_{i}  &  &  & $-$0.798 &  &  & $-$1.172 \\ 
  &  &  & (1.162) &  &  & (1.167) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Yes fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

>>>>

\begin{document}% Date and time \times Sat, Apr 04, 2020 - 15:22:31
\begin{table}[!htbp] \centering 
  \caption{Presence of Foreign firms} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable \times \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.422$^{*}$ & $-$0.521$^{*}$ & $-$0.356 & $-$0.186 & $-$0.274 & $-$0.347 \\ 
  & (0.228) & (0.288) & (0.258) & (0.296) & (0.347) & (0.305) \\ 
   TCZ_c \times \text{Period} \times \text{output share Foreign}_{i} & $-$0.647 &  &  & 0.326 &  &  \\ 
  & (0.756) &  &  & (1.090) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{output share SOE}_{i} \_ & $-$0.377 &  &  & $-$0.844 &  &  \\ 
  & (0.466) &  &  & (0.597) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share Foreign}_{i} & 0.719 &  &  & $-$0.626 &  &  \\ 
  & (1.097) &  &  & (1.406) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i} \_ & 1.069$^{*}$ &  &  & 1.030 &  &  \\ 
  & (0.568) &  &  & (0.673) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{capital share Foreign}_{i}  &  & $-$0.525 &  &  & 0.109 &  \\ 
  &  & (0.805) &  &  & (0.995) &  \\ 
   TCZ_c \times \text{Period} \times \text{capital share SOE}_{i} \_ &  & $-$0.209 &  &  & $-$0.751 &  \\ 
  &  & (0.406) &  &  & (0.495) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share Foreign}_{i}  &  & 1.094 &  &  & $-$0.527 &  \\ 
  &  & (1.156) &  &  & (1.401) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i} \_ &  & 0.827 &  &  & 0.918 &  \\ 
  &  & (0.536) &  &  & (0.606) &  \\ 
   TCZ_c \times \text{Period} \times \text{labour share Foreign}_{i}  &  &  & $-$0.129 &  &  & 0.475 \\ 
  &  &  & (0.737) &  &  & (0.983) \\ 
   TCZ_c \times \text{Period} \times \text{labour share SOE}_{i} \_ &  &  & $-$0.177 &  &  & $-$0.843 \\ 
  &  &  & (0.455) &  &  & (0.601) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share Foreign}_{i}  &  &  & 0.230 &  &  & 0.014 \\ 
  &  &  & (1.314) &  &  & (1.399) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i} \_ &  &  & 0.778 &  &  & 1.154$^{*}$ \\ 
  &  &  & (0.567) &  &  & (0.664) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Yes fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

### 2020-04-27 Temp_tables/Temp_tables_revision/03_Paper_version_Revised/05_table_8_rob_4.tex
back up before new paper

\begin{document}% Date and time: Sat, Apr 04, 2020 - 11:27:39
\begin{table}[!htbp] \centering 
  \caption{Presence of Foreign firms} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.101 & $-$0.101 & $-$0.051 & 0.078 & 0.123 & 0.044 \\ 
  & (0.169) & (0.164) & (0.156) & (0.211) & (0.203) & (0.180) \\ 
   TCZ_c \times \text{Period} \times \text{output share Foreign}_{i} & $-$0.387 &  &  & 0.937 &  &  \\ 
  & (0.662) &  &  & (0.919) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share Foreign}_{i} & $-$0.299 &  &  & $-$1.448 &  &  \\ 
  & (1.019) &  &  & (1.237) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{capital share Foreign}_{i}  &  & $-$0.291 &  &  & 0.984 &  \\ 
  &  & (0.620) &  &  & (0.781) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share Foreign}_{i}  &  & $-$0.249 &  &  & $-$1.710 &  \\ 
  &  & (0.942) &  &  & (1.109) &  \\ 
   TCZ_c \times \text{Period} \times \text{labour share Foreign}_{i}  &  &  & 0.004 &  &  & 1.203 \\ 
  &  &  & (0.599) &  &  & (0.757) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share Foreign}_{i}  &  &  & $-$0.798 &  &  & $-$1.172 \\ 
  &  &  & (1.162) &  &  & (1.167) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Yes fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

>>>>

\begin{document}% Date and time: Sat, Apr 04, 2020 - 12:53:19
\begin{table}[!htbp] \centering 
  \caption{Concentration of industry} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{6}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-7} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6)\\
 \\[-1.8ex]& Output & Capital & Labour & Output & Capital & Labour\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.032 & $-$0.142 & $-$0.097 & 0.086 & 0.037 & 0.060 \\ 
  & (0.639) & (0.643) & (0.635) & (0.698) & (0.688) & (0.679) \\ 
   TCZ_c \times \text{Period} \times \text{Herfindahl}_{i} & 0.029 & 0.013 & 0.013 & 0.451 & 0.491 & 0.528 \\ 
  & (0.819) & (0.810) & (0.818) & (0.946) & (0.943) & (0.914) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{Herfindahl}_{i} & $-$0.404 & $-$0.240 & $-$0.345 & $-$0.597 & $-$0.582 & $-$0.687 \\ 
  & (0.932) & (0.937) & (0.931) & (1.034) & (1.019) & (1.001) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}  & 1.216$^{**}$ &  &  & 1.478$^{**}$ &  &  \\ 
  & (0.586) &  &  & (0.649) &  &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i}  &  & 0.787$^{*}$ &  &  & 1.175$^{**}$ &  \\ 
  &  & (0.459) &  &  & (0.541) &  \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}  &  &  & 1.048$^{*}$ &  &  & 1.702$^{***}$ \\ 
  &  &  & (0.572) &  &  & (0.612) \\ 
 \hline \\[-1.8ex] 
City fixed effects & Yes & Yes & Yes & No & No & No \\ 
Industry fixed effects & Yes & Yes & Yes & No & No & No \\ 
Yes fixed effects & Yes & Yes & Yes & No & No & No \\ 
City-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
Industry-year fixed effects & No & No & No & Yes & Yes & Yes \\ 
City-industry fixed effects & No & No & No & Yes & Yes & Yes \\ 
Observations & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 & 30,676 \\ 
R$^{2}$ & 0.346 & 0.346 & 0.346 & 0.851 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

### 2020-04-27 Temp_tables/Temp_tables_revision/03_Paper_version_Revised/07_table_9_size_capital.tex
back up before new paper

\begin{document}% Date and time: Sat, Apr 04, 2020 - 13:32:33
\begin{table}[!htbp] \centering 
  \caption{Deciles output} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{10}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-11} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9 &  Baseline\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.614 & $-$0.360 & $-$0.438$^{**}$ & $-$0.438$^{**}$ & $-$0.370$^{**}$ & $-$0.355$^{**}$ & $-$0.329$^{**}$ & $-$0.300$^{**}$ & $-$0.307$^{**}$ & $-$0.298$^{**}$ \\ 
  & (0.461) & (0.227) & (0.196) & (0.177) & (0.165) & (0.148) & (0.143) & (0.142) & (0.141) & (0.142) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{output share SOE}_{i}  & 3.972 & 3.288$^{**}$ & 2.158$^{*}$ & 2.236$^{**}$ & 1.722$^{**}$ & 1.544$^{*}$ & 1.513$^{**}$ & 1.259$^{*}$ & 1.345$^{**}$ & 1.315$^{**}$ \\ 
  & (2.733) & (1.490) & (1.140) & (1.035) & (0.862) & (0.788) & (0.698) & (0.676) & (0.613) & (0.609) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 7,646 & 13,563 & 17,682 & 22,109 & 25,418 & 28,062 & 29,422 & 30,132 & 30,388 & 30,676 \\ 
R$^{2}$ & 0.877 & 0.860 & 0.853 & 0.845 & 0.846 & 0.847 & 0.848 & 0.850 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank of the city-industry concentration (Herfhindal index) \
More specifically, the low deciles means a low concentration by city-industry \
Deciles close to one, however, implies a stronger concentration.
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

>>>>

\begin{document}% Date and time: Sat, Apr 04, 2020 - 13:38:12
\begin{table}[!htbp] \centering 
  \caption{Deciles capital} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{10}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-11} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9 &  Baseline\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.610 & $-$0.342 & $-$0.467$^{**}$ & $-$0.467$^{**}$ & $-$0.406$^{**}$ & $-$0.401$^{**}$ & $-$0.368$^{**}$ & $-$0.337$^{**}$ & $-$0.343$^{**}$ & $-$0.336$^{**}$ \\ 
  & (0.533) & (0.253) & (0.213) & (0.202) & (0.190) & (0.168) & (0.155) & (0.154) & (0.154) & (0.154) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i}  & 2.183 & 1.785 & 1.380 & 1.545$^{*}$ & 1.289$^{*}$ & 1.245$^{*}$ & 1.192$^{**}$ & 1.027$^{*}$ & 1.073$^{**}$ & 1.065$^{**}$ \\ 
  & (2.064) & (1.099) & (0.844) & (0.827) & (0.732) & (0.656) & (0.548) & (0.529) & (0.515) & (0.513) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 7,646 & 13,563 & 17,682 & 22,109 & 25,418 & 28,062 & 29,422 & 30,132 & 30,388 & 30,676 \\ 
R$^{2}$ & 0.877 & 0.860 & 0.853 & 0.845 & 0.846 & 0.847 & 0.848 & 0.850 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank of the city-industry concentration (Herfhindal index) \
More specifically, the low deciles means a low concentration by city-industry \
Deciles close to one, however, implies a stronger concentration.
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

### 2020-04-27 Temp_tables/Temp_tables_revision/03_Paper_version_Revised/08_table_9_size_employement.tex
back up before new paper

\begin{document}% Date and time: Sat, Apr 04, 2020 - 13:38:12
\begin{table}[!htbp] \centering 
  \caption{Deciles capital} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{10}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-11} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9 &  Baseline\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.610 & $-$0.342 & $-$0.467$^{**}$ & $-$0.467$^{**}$ & $-$0.406$^{**}$ & $-$0.401$^{**}$ & $-$0.368$^{**}$ & $-$0.337$^{**}$ & $-$0.343$^{**}$ & $-$0.336$^{**}$ \\ 
  & (0.533) & (0.253) & (0.213) & (0.202) & (0.190) & (0.168) & (0.155) & (0.154) & (0.154) & (0.154) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{capital share SOE}_{i}  & 2.183 & 1.785 & 1.380 & 1.545$^{*}$ & 1.289$^{*}$ & 1.245$^{*}$ & 1.192$^{**}$ & 1.027$^{*}$ & 1.073$^{**}$ & 1.065$^{**}$ \\ 
  & (2.064) & (1.099) & (0.844) & (0.827) & (0.732) & (0.656) & (0.548) & (0.529) & (0.515) & (0.513) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 7,646 & 13,563 & 17,682 & 22,109 & 25,418 & 28,062 & 29,422 & 30,132 & 30,388 & 30,676 \\ 
R$^{2}$ & 0.877 & 0.860 & 0.853 & 0.845 & 0.846 & 0.847 & 0.848 & 0.850 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank of the city-industry concentration (Herfhindal index) \
More specifically, the low deciles means a low concentration by city-industry \
Deciles close to one, however, implies a stronger concentration.
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}

>>>>

\begin{document}% Date and time: Sat, Apr 04, 2020 - 13:38:24
\begin{table}[!htbp] \centering 
  \caption{Deciles Employement} 
\label{}
\begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{tabular}{@{\extracolsep{5pt}}lcccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{10}{c}{Dependent variable: \text { SO2 emission }_{i k t}} \\ 
\cline{2-11} 
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10)\\
 \\[-1.8ex]& decile .1 & decile .2 &  decile .3 & decile .4 & decile .5 & decile .6 &  decile .7 & decile .8 & decile .9 &  Baseline\\
 \hline \\[-1.8ex] 
   TCZ_c \times \text{Period} \times \text{Polluted}_i  & $-$0.897$^{*}$ & $-$0.442$^{*}$ & $-$0.524$^{**}$ & $-$0.533$^{***}$ & $-$0.472$^{***}$ & $-$0.454$^{***}$ & $-$0.417$^{***}$ & $-$0.380$^{**}$ & $-$0.386$^{**}$ & $-$0.377$^{**}$ \\ 
  & (0.497) & (0.254) & (0.209) & (0.191) & (0.182) & (0.162) & (0.156) & (0.155) & (0.153) & (0.154) \\ 
   TCZ_c \times \text{Period} \times \text{Polluted}_i \times \text{labour share SOE}_{i}  & 4.633$^{*}$ & 2.815$^{**}$ & 2.105$^{**}$ & 2.336$^{**}$ & 2.024$^{**}$ & 1.847$^{**}$ & 1.764$^{***}$ & 1.512$^{**}$ & 1.553$^{***}$ & 1.532$^{**}$ \\ 
  & (2.435) & (1.385) & (0.998) & (0.919) & (0.832) & (0.734) & (0.668) & (0.650) & (0.601) & (0.598) \\ 
 \hline \\[-1.8ex] 
City-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Industry-year fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
City-industry fixed effects & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes & Yes \\ 
Observations & 7,646 & 13,563 & 17,682 & 22,109 & 25,418 & 28,062 & 29,422 & 30,132 & 30,388 & 30,676 \\ 
R$^{2}$ & 0.878 & 0.860 & 0.853 & 0.845 & 0.846 & 0.847 & 0.848 & 0.850 & 0.851 & 0.851 \\ 
\hline 
\hline \\[-1.8ex] 
\end{tabular}
\end{adjustbox}
\begin{tablenotes} 
 \small 
 \item \\ 
\footnotesize{
A decile indicates the rank of the city-industry concentration (Herfhindal index) \
More specifically, the low deciles means a low concentration by city-industry \
Deciles close to one, however, implies a stronger concentration.
Due to limited space, only the coefficients of interest are presented 
for the regressions with city,industry, year fixed effect (i.e. columns 1-3).
\sym{*} Significance at the 10\%, \sym{**} Significance at the 5\%, \sym{***} Significance at the 1\% \
heteroscedasticity-robust standard errors in parentheses are clustered by city 
}
